Automating Verification of MPC Security

### 2023-06-20 popl24/minicat.tex
checkpoint
typos

\section{The $\minifed$ Language}

@@

We model probabilistic programming via the \emph{random tape}
approach. That is, we will assume that programs can make reference to
values chosen from a uniform random distribution- coin ``flips''- via
values arbitrarily assigned in the initial program memory.  Programs
execute deterministically given the random tape. The random tape
formulation supports our automated analysis as we discuss in
section

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed-syntax}, includes a standard boolean algebra
with $\eand$, $\eor$, $\exor$, and $\enot$ as primitives. In addition
programs have different kinds of variables, including \emph{secrets}
$\secret{\cid}{w}$, \emph{flips} $\flip{\cid}{w}$, and \emph{views}
$\view{\cid}{w}$.  Each of these variables are indexed by an ``owner''
client $\cid$ and distinguishing string $w$. So for example,
$\secret{\ttt{1}}{\ttt{foo}}$ is client $\ttt{1}$'s secret called
$\ttt{foo}$. All clients can make reference to the \emph{oracle}
through variables $\oracle{w}$- this is a form of shared randomness
that is standard in the MPC setting \cite{evans2018pragmatic}.  Each client can only
compute on their own variables in \emph{expressions} $\be$, and share
values with other clients by assignment to their views as in
$\eassign{\view{\cid}{w}}{\be}$.  A \emph{protocol} $\prog$ is a
possibly empty sequence of view assignments. We will generally omit
$\varnothing$ from example code, writing $\instr_1;\ldots;\instr_n$
instead of $\instr_1;\ldots;\instr_n;\varnothing$, and abusing notation we will
write $\prog_1;\prog_2$ to denote the concatenation of $\prog_1$
and $\prog_2$.

@@

Expressions forms include the convenience
$\select{\be_1}{\be_2}{\be_3}$ which is essentially a conditional
expression with:
$$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$$
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However its inclusion simplifies our presentation and is a useful
convenience.

@@

Given a set of variables $X$, we write $\store_X$ to denoted the
memory $\store$ restricted to the domain $X$, and and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories with the same domain, and abusing notation
we write $\dom(\stores)$ to denote the common domain,
and $\stores_X \defeq \{ \store_X | \store \in \stores \}$.

@@

Here we introduce some examples to illustrate $\minifed$ and how it
can be used to model secure communication protocols for values in the
binary field. Most of these are translations (into $\minifed$) of
object examples in previous related work
\cite{barthe2019probabilistic,darais2019language}.  We will return to
these as running examples throughout the paper to illustrate various
concepts and advantages of our methods. In Section
\ref{section-metalang} we will formulate a larger example
implementation of Yao's Garbled Circuits (Example \ref{example-ygc}).
\begin{example}[One-Time Pad]
  \label{example-otp}
As observed in \cite{barthe2019probabilistic} and elsewhere, coin flips with $\exor$ can
be used to model one-time pad encryption in the binary field. On the
basis of this we can model secure communication between over an
insecure channel using symmetric key encryption. In the following
program, we assume $H = \{ 1,2 \}$ and $C = \{ 0 \}$. Client 1 first
shares the randomly generated ``key'' $\fx{1}{0}$ with client 2
through view $\view{2}{0}$. Then, client 1 encrypts its secret
$\sx{1}{0}$ and sends it to party 0, which relays the ciphertext in
$\vx{0}{0}$ to client 2. Finally, client 2 decrypts the the ciphertext
and stores the plaintext in $\vx{2}{2}$.
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
Intuitively, this protocol is \emph{correct} because $\vx{2}{2}$ is
exactly correlated with the secret $\sx{1}{0}$, and it is
\emph{secure} because the corrupt view $\vx{0}{0}$ in isolation is
probabilistically independent of the secret $\sx{1}{0}$.
\end{example}

>>>>

\section{The $\minifed$ Language}
\label{section-minicat}

@@

We model probabilistic programming via the \emph{random tape}
approach. That is, we will assume that programs can make reference to
values chosen from a uniform random distribution- coin ``flips''- via
values arbitrarily assigned in the initial program memory.  Programs
execute deterministically given the random tape. The random tape
formulation supports our automated analysis as we discuss in
section \dnote{5?}

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed-syntax}, includes a standard boolean algebra
with $\eand$, $\eor$, $\exor$, and $\enot$ as primitives. In addition,
programs have different kinds of variables including \emph{secrets}
$\secret{\cid}{w}$, \emph{flips} $\flip{\cid}{w}$, and \emph{views}
$\view{\cid}{w}$.  Each of these variables are indexed by an ``owner''
client $\cid$ and distinguishing string $w$. So for example,
$\secret{\ttt{1}}{\ttt{foo}}$ is client $\ttt{1}$'s secret called
$\ttt{foo}$. All clients can make reference to the \emph{oracle}
through variables $\oracle{w}$- this is a form of shared randomness
that is standard in the MPC setting \cite{evans2018pragmatic}.  Each client can only
compute on their own variables in \emph{expressions} $\be$, and share
values with other clients by assignment to their views as in
$\eassign{\view{\cid}{w}}{\be}$.  A \emph{protocol} $\prog$ is a
possibly empty sequence of view assignments. We will generally omit
$\varnothing$ from example code, writing $\instr_1;\ldots;\instr_n$
instead of $\instr_1;\ldots;\instr_n;\varnothing$, and abusing notation we will
write $\prog_1;\prog_2$ to denote the concatenation of $\prog_1$
and $\prog_2$.

@@

Expression forms include the convenience
$\select{\be_1}{\be_2}{\be_3}$, which is essentially a conditional
expression with:
$$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$$
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However its inclusion simplifies our presentation and is a useful
convenience.

@@

Given a set of variables $X$, we write $\store_X$ to denote the
memory $\store$ restricted to the domain $X$, and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories with the same domain, and abusing notation
we write $\dom(\stores)$ to denote the common domain,
and $\stores_X \defeq \{ \store_X | \store \in \stores \}$.

@@

Here we introduce some examples to illustrate $\minifed$ and how it
can be used to model secure communication protocols for values in the
binary field. Most of these are translations (into $\minifed$) of
object examples in previous related work
\cite{barthe2019probabilistic,darais2019language}.  We will return to
these as running examples throughout the paper to illustrate various
concepts and advantages of our methods. In Section
\ref{section-metalang} we will formulate a larger example
implementation of Yao's Garbled Circuits.
\begin{example}[One-Time Pad]
  \label{example-otp}
As observed in \cite{barthe2019probabilistic} and elsewhere, coin flips with $\exor$ can
be used to model one-time pad encryption in the binary field. On the
basis of this we can model secure communication between over an
insecure channel using symmetric key encryption. In the following
program, we assume $H = \{ 1,2 \}$ and $C = \{ 0 \}$. Client 1 first
shares the randomly generated ``key'' $\fx{1}{0}$ with client 2
through view $\view{2}{0}$. Then, client 1 encrypts its secret
$\sx{1}{0}$ and sends it to party 0, which relays the ciphertext in
$\vx{0}{0}$ to client 2. Finally, client 2 decrypts the the ciphertext
and stores the plaintext in $\vx{2}{2}$.
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
Intuitively, this protocol is \emph{correct} because $\vx{2}{2}$ is
exactly correlated with the secret $\sx{1}{0}$, and it is
\emph{secure} because the corrupt view $\vx{0}{0}$ in isolation is
probabilistically independent of the secret $\sx{1}{0}$.
\end{example}

### 2023-06-20 popl24/pmf.tex
typos

In order to precisely characterize distributions of secrets and views
in programs we define probability mass functions in a standard manner,
following the formulation in \ref{barthe2019probabilistic}. In this formulation, memories
denote conjunctions of variable assignments. Intuitively, given a
program $\prog$ with $\iov(\prog) = S \cup V$ and $\store \in
\mems(\iov(\prog))$, when considering the execution of $\prog$
initialized with secrets $\store_S$, we are fundamentally concerned
with the joint probability of the assignments in $\store_V$
conditioned by the assignments $\store_S$. This is because
probabilistic dependence between honest secrets and corrupt views
\emph{is} information leakage.

@@

\subsection{Program Distributions}
Now we can define the probability distribution of a program $\prog$,
that we denote $\progd(\prog)$. Since $\fedcat$ is deterministic the
results (view assignments) of any run are determined by the input
secrets together with the random tape. And since we constrain programs
to not overwrite views we are assured that \emph{final} memories
contain both a complete record of all initial secrets as well as views
resulting from communicated information.

>>>>

In order to precisely characterize distributions of secrets and views
in programs, we define probability mass functions in a standard manner,
following the formulation in \ref{barthe2019probabilistic}. In this formulation, memories
denote conjunctions of variable assignments. Intuitively, given a
program $\prog$ with $\iov(\prog) = S \cup V$ and $\store \in
\mems(\iov(\prog))$, when considering the execution of $\prog$
initialized with secrets $\store_S$, we are fundamentally concerned
with the joint probability of the assignments in $\store_V$
conditioned by the assignments $\store_S$. This is because
probabilistic dependence between honest secrets and corrupt views
\emph{is} information leakage.

@@

\subsection{Program Distributions}
Now we can define the probability distribution of a program $\prog$,
that we denote $\progd(\prog)$. Since $\fedcat$ is deterministic the
results (view assignments) of any run are determined by the input
secrets together with the random tape. And since we constrain programs
to not overwrite views, we are assured that \emph{final} memories
contain both a complete record of all initial secrets as well as views
resulting from communicated information.
